% Main Manuscript File - EES Submission
% Quantum Spectral Engineering for Enhanced Agrivoltaic Efficiency

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts,graphicx,booktabs,bm,multirow,siunitx,physics}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{natbib}
\usepackage[margin=2.cm]{geometry}

% Hyperref setup
\hypersetup{
    pdftitle={Quantum Spectral Engineering for Enhanced Agrivoltaic Efficiency - Main Manuscript},
    pdfauthor={Teguia et al.},
    pdfsubject={Quantum Photosynthesis, Agrivoltaics, Non-Markovian Dynamics},
    pdfkeywords={agrivoltaics, quantum photosynthesis, spectral engineering, non-Markovian dynamics, renewable energy},
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\DeclareSIUnit{\yr}{yr}
\DeclareSIUnit{\tonne}{t}
\DeclareSIUnit{\hectare}{ha}
\DeclareSIUnit{\kWh}{kWh}

%=============================================================================
% TITLE AND AUTHORS
%=============================================================================

\title{\textbf{Quantum Spectral Engineering for Enhanced Agrivoltaic Efficiency: Non-Markovian Dynamics in Photosynthetic Energy Transfer}}

\author{
    Steve Cabrel Teguia Kouam$^{2,*}$,
    Theodore Goumai Vedekoi$^{1}$, 
    Jean-Pierre Tchapet Njafa$^{1}$, \\
    Jean-Pierre Nguenang$^{2}$,
    Serge Guy Nana Engo$^{1}$ \\
    \\
    $^{1}$Department of Physics, Faculty of Science, University of Yaoundé I, Cameroon \\
    $^{2}$Department of Physics, Faculty of Science, University of Douala, Cameroon \\
    \\
    $^{*}$Corresponding author: \texttt{steve.teguia@univ-douala.cm}
}

\date{\today}

%=============================================================================
% DOCUMENT BEGIN
%=============================================================================

\begin{document}

\maketitle

%=============================================================================
% ABSTRACT
%=============================================================================

\begin{abstract}
Agrivoltaic systems integrate crop production with solar energy generation, addressing the critical energy-environment nexus of food security and clean energy. Current designs treat light as a classical photon flux, overlooking the quantum mechanical aspects of photosynthetic energy transfer that could enhance both energy efficiency and agricultural productivity. We introduce \textit{spectral bath engineering}---strategic spectral filtering through semi-transparent organic photovoltaic (OPV) panels to exploit non-Markovian quantum coherence in photosynthesis. Using adaptive Hierarchy of Pure States (adHOPS) simulations of the Fenna-Matthews-Olsen complex, we demonstrate that selective filtering at vibronic resonance wavelengths (\SIlist{750;820}{\nano\meter} dual-band) enhances the electron transport rate (ETR) by \SI{25}{\percent} relative to Markovian models under matched photon flux. This quantum advantage stems from vibronic resonance-assisted transport that extends coherence lifetimes by \SIrange{20}{50}{\percent}, nearly doubles pairwise concurrence (\SI{+89}{\percent}), and extends exciton delocalization from \numrange{3}{5} to \numrange{8}{10} chromophores. A comprehensive 12-test validation suite confirms robustness at \SI{295}{\kelvin} and under static disorder ($\sigma = \SI{50}{\per\cm}$). Geographic simulations across nine climate zones---including five sub-Saharan African sites---demonstrate persistent quantum advantages of \SIrange{18}{26}{\percent}, with particular relevance to regions where energy and food security challenges converge. Pareto optimization identifies configurations achieving \SIrange{16}{18}{\percent} power conversion efficiency with \SIrange{15}{20}{\percent} ETR enhancement, yielding an estimated additional revenue of USD~\numrange{470}{3000}\,\si{ha^{-1}\,yr^{-1}}. Integration with eco-design analysis using quantum reactivity descriptors ensures environmental sustainability with biodegradable OPV materials (biodegradability scores of \num{0.72} for PM6 derivative and 0.58 for Y6-BO derivative, confirming $B_{\rm index} = \num{72}$ and $B_{\rm index} = \num{58}$ respectively), addressing the critical environmental sustainability requirements of next-generation energy technologies.
\end{abstract}

%=============================================================================
% BROADER CONTEXT
%=============================================================================
\noindent\textbf{Broader context}

Meeting rising global demand for food and clean energy requires new approaches to land-use optimization that address the critical energy-environment nexus. Agrivoltaic systems co-locate solar panels with crop production, yet existing designs rely on classical optics that ignore biological light use at the molecular level. In photosynthetic pigment-protein complexes, energy transfer is governed by quantum mechanical processes sensitive to the spectral composition of incident light. We demonstrate that engineering the transmission spectrum of semi-transparent solar panels to target specific vibronic resonances enhances biological energy transfer efficiency while generating electricity. This quantum spectral bath engineering approach bridges quantum biology and renewable energy engineering, providing quantitative design rules for next-generation agrivoltaic materials that improve both crop productivity and solar yields while maintaining environmental sustainability through eco-design analysis using quantum reactivity descriptors (biodegradability scores of 0.72 for PM6 derivative and 0.58 for Y6-BO derivative). This work addresses UN SDGs 2 (Zero hunger), 7 (Affordable and clean energy), and 13 (Climate action) by demonstrating how quantum effects can be leveraged to optimize the energy conversion efficiency of natural photosynthetic systems, with particular relevance to regions where energy and food security challenges converge.

\vspace{1em}

%=============================================================================
% KEYWORDS
%=============================================================================

\noindent\textbf{Keywords:} Agrivoltaics, Quantum photosynthesis, Spectral engineering, Non-Markovian dynamics, Renewable energy, Organic photovoltaics, Coherence-assisted transport, Sustainable agriculture

%=============================================================================
% MAIN CONTENT (MODULAR SECTIONS)
%=============================================================================

\input{files2/introduction}

\input{files2/theory_methods}

\input{files2/results}

\input{files2/discussion}

\input{files2/conclusion}

%=============================================================================
% ACKNOWLEDGMENTS
%=============================================================================

\section*{Acknowledgments}

This work was supported by the University of Yaoundé I and the University of Douala. We thank the MesoHOPS development team for providing open-source software enabling these simulations. 

%=============================================================================
% DATA AVAILABILITY
%=============================================================================

\section*{Data availability statement}

All data supporting the findings of this study are available within the article and its Supporting Information. Raw simulation output files, analysis scripts, and parameter sets are available from the corresponding author upon reasonable request. The MesoHOPS simulation package used in this work is freely available at \url{https://github.com/MesoscienceLab/mesohops}. All computational notebooks, source code, and datasets generated during this study are available in the GitHub repository at [REPOSITORY_URL]. Reproducibility information: All simulations were performed using Python 3.12.12, NumPy 1.24+, SciPy 1.11+, and the MesoHOPS v1.2.0 library. Computational parameters and environment configurations are documented in the Supporting Information. All reported values include standard errors calculated from ensemble averaging, with 95\% confidence intervals explicitly stated for all quantitative results.

%=============================================================================
% CONFLICTS OF INTEREST
%=============================================================================

\section*{Conflicts of Interest}

The authors declare no conflicts of interest.

%=============================================================================
% AUTHOR CONTRIBUTIONS
%=============================================================================

\section*{Author Contributions}

\textbf{Steve Cabrel Teguia Kouam}: Methodology, Validation, Formal analysis, Writing -- original draft. \textbf{Theodore Goumai Vedekoi}: Software, Investigation, Data curation, Writing -- original draft. \textbf{Jean-Pierre Tchapet Njafa}: Conceptualization, Theoretical framework, Writing -- review \& editing. \textbf{Jean-Pierre Nguenang}: Resources, Supervision, Formal analysis. \textbf{Serge Guy Nana Engo}: Project administration, Conceptualization, Theoretical framework, final Manuscript editing. All authors have given approval to the final version of the manuscript.

%=============================================================================
% REFERENCES
%=============================================================================

\bibliographystyle{unsrt}  % Numbered references per RSC style
\bibliography{references}  % BibTeX file with all references

%=============================================================================
% SUPPORTING INFORMATION
%=============================================================================

\section*{Supporting Information}

Supporting Information includes detailed environmental factor models, biodegradability assessment, extended validation data (12 tests), complete FMO parameter sets, computational performance benchmarks, and supplementary figures S1--S8.

%=============================================================================
\end{document}
%=============================================================================
